A game of competition over risk

### 2023-04-17 paper/article.tex
Updates from Overleaf

\usepackage{hyperref}
\usepackage{svg}
\usepackage{float}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\begin{figure}[htbp]
    \centering
    \includesvg[width=0.8\linewidth]{plots/reward}
    \caption{Reward function}
    \label{fig:reward}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/nash-0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/nash-1}
  \end{minipage}
  \caption{Nash equilibrium}
  \label{fig:nash}  
\end{figure}

\begin{figure}[htbp]
  \centering
  \includesvg[width=0.8\linewidth]{plots/cutoff}
  \caption{The cutoff goes to zero when $C \rightarrow\infty$.}
  \label{fig:cutoff}  
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/solution-multiple-0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/solution-multiple-1}
  \end{minipage}
  \caption{We observe a clear difference between the cases $C=0$ (no penalty) and $C=1$ (presence of a penalty). In both cases, the cutoff increases. However, the average risk seems to decrease sharply when there is a nonzero penalty with a mode at $r=0$.}
  \label{fig:solution-multiple}  
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includesvg[width=0.8\linewidth]{plots/cutoff-asymptotic}
    \caption{The plot of $r_{max}$ to $\log(C)$ is very similar to the function $\frac{1}{1 + \exp(\cdot)}$. This is because $r_{max} \sim \frac{1}{1+C}$.}
    \label{fig:cutoff-asymptotic}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includesvg[width=0.8\linewidth]{plots/efficiency}
    \caption{The efficiency clearly goes to $0$ even when $e = 1$. When $e>1$, it seems that $E \rightarrow 1$. Values for greater values of $n$ suffer of numerical precision issues as $\log w \rightarrow 0$.}
    \label{fig:efficiency}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/linear-dmax-shift}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/linear-lambda-shift}
  \end{minipage}
  \caption{We observe that for almost all values of the parameters, $d_{max}$ is numerically zero. $\lambda$ is computed for a correlated equilibrium that maximizes the total reward. We cross out cases where the solver failed to find a solution, most probably due to rounding errors which caused the small solution set to disappear. In the few cases where $d_{max}$ was not observed to be zero, $\lambda$ is clearly zero, which shows that the best correlated equilibrium is a Nash equilibrium. We also interpret the nonzero values of $d_{max}$}
  \label{fig:linear-shift}  
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/regret_matching_methods_nashconv}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/regret_matching_methods_quasinashconv}
  \end{minipage}
  \caption{Evaluation of different algorithms to find Nash equilibrium in the standard setting $P=R=1, \sigma=0, \rho=0$ without sharing. The game was reduced to a grid of $a=2^{12}$ actions and \textsc{QuasiNashConv} was evaluated on $2^{15}$ points. The algorithms ran for $10^4$ iterations. For CFR, an iteration is an update to the strategy. For regret matching, we define an iteration as $a$ steps of the sampling, play and update process, so that both CFR and RM do $\mathcal{O}(a^2)$ operations per iteration. We do not include the computation of the utility matrix in the computation time.}
  \label{fig:rm-different}  
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/regret_matching_sizes_nashconv}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/regret_matching_sizes_quasinashconv}
  \end{minipage}
  \caption{Performance of the vanilla regret matching algorithm to find Nash equilibrium in the standard setting $P=R=1, \sigma=0, \rho=0$ without sharing. The quality of the resulting equilibrium depends mainly on the number of actions $a$. For $t$ iterations, the time complexity of the algorithm is $\mathcal{O}(t a^2)$ and the memory complexity is $\mathcal{O}(a^2)$ as it requires to compute the reward matrix. \textsc{QuasiNashConv} was evaluated on $8 a$ points.}
  \label{fig:rm-size}  
\end{figure}

@@

\begin{figure}[H]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/nash-0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/nash-0.5}
  \end{minipage}
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/nash-1}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/nash-10}
  \end{minipage}
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/nash-100}
  \end{minipage}
  \hfill
\end{figure}

@@

\begin{figure}[H]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/linear-dmax-no-shift}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{plots/linear-lambda-no-shift}
  \end{minipage}
\end{figure}

>>>>

\usepackage{hyperref}
\usepackage{svg}

\svgpath{{../plots/}}

\usepackage{float}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\begin{figure}[htbp]
    \centering
    \includesvg[width=0.8\linewidth]{reward}
    \caption{Reward function}
    \label{fig:reward}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{nash-0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{nash-1}
  \end{minipage}
  \caption{Nash equilibrium}
  \label{fig:nash}  
\end{figure}

\begin{figure}[htbp]
  \centering
  \includesvg[width=0.8\linewidth]{cutoff}
  \caption{The cutoff goes to zero when $C \rightarrow\infty$.}
  \label{fig:cutoff}  
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{solution-multiple-0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{solution-multiple-1}
  \end{minipage}
  \caption{We observe a clear difference between the cases $C=0$ (no penalty) and $C=1$ (presence of a penalty). In both cases, the cutoff increases. However, the average risk seems to decrease sharply when there is a nonzero penalty with a mode at $r=0$.}
  \label{fig:solution-multiple}  
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includesvg[width=0.8\linewidth]{cutoff-asymptotic}
    \caption{The plot of $r_{max}$ to $\log(C)$ is very similar to the function $\frac{1}{1 + \exp(\cdot)}$. This is because $r_{max} \sim \frac{1}{1+C}$.}
    \label{fig:cutoff-asymptotic}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includesvg[width=0.8\linewidth]{efficiency}
    \caption{The efficiency clearly goes to $0$ even when $e = 1$. When $e>1$, it seems that $E \rightarrow 1$. Values for greater values of $n$ suffer of numerical precision issues as $\log w \rightarrow 0$.}
    \label{fig:efficiency}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{linear-dmax-shift}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{linear-lambda-shift}
  \end{minipage}
  \caption{We observe that for almost all values of the parameters, $d_{max}$ is numerically zero. $\lambda$ is computed for a correlated equilibrium that maximizes the total reward. We cross out cases where the solver failed to find a solution, most probably due to rounding errors which caused the small solution set to disappear. In the few cases where $d_{max}$ was not observed to be zero, $\lambda$ is clearly zero, which shows that the best correlated equilibrium is a Nash equilibrium. We also interpret the nonzero values of $d_{max}$}
  \label{fig:linear-shift}  
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{regret_matching_methods_nashconv}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{regret_matching_methods_quasinashconv}
  \end{minipage}
  \caption{Evaluation of different algorithms to find Nash equilibrium in the standard setting $P=R=1, \sigma=0, \rho=0$ without sharing. The game was reduced to a grid of $a=2^{12}$ actions and \textsc{QuasiNashConv} was evaluated on $2^{15}$ points. The algorithms ran for $10^4$ iterations. For CFR, an iteration is an update to the strategy. For regret matching, we define an iteration as $a$ steps of the sampling, play and update process, so that both CFR and RM do $\mathcal{O}(a^2)$ operations per iteration. We do not include the computation of the utility matrix in the computation time.}
  \label{fig:rm-different}  
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{regret_matching_sizes_nashconv}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{regret_matching_sizes_quasinashconv}
  \end{minipage}
  \caption{Performance of the vanilla regret matching algorithm to find Nash equilibrium in the standard setting $P=R=1, \sigma=0, \rho=0$ without sharing. The quality of the resulting equilibrium depends mainly on the number of actions $a$. For $t$ iterations, the time complexity of the algorithm is $\mathcal{O}(t a^2)$ and the memory complexity is $\mathcal{O}(a^2)$ as it requires to compute the reward matrix. \textsc{QuasiNashConv} was evaluated on $8 a$ points.}
  \label{fig:rm-size}  
\end{figure}

@@

\begin{figure}[H]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{nash-0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{nash-0.5}
  \end{minipage}
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{nash-1}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{nash-10}
  \end{minipage}
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{nash-100}
  \end{minipage}
  \hfill
\end{figure}

@@

\begin{figure}[H]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{linear-dmax-no-shift}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{linear-lambda-no-shift}
  \end{minipage}
\end{figure}
